DOpElib: Differential Equations\\ and Optimization Environment

### 2013-11-18 Examples/OPT/StatPDE/Example9/content.tex

The target functional is considered as 
\[
k(U) = \int_{\hat\Gamma_O \cup \hat\Gamma_i} \hat n\cdot \hat J\hat\sigma(v,p)\hat
F^{-T} \cdot \hat d \, ds,
\]
where $\Gamma_O$ denotes the cylinder boundary and $\Gamma_i$ the 
interface between fluid and solid, and $\hat d$ is a vector in the
direction
of the mean flow. Moreover, $\hat J$ and $\hat F$ denote the deformation 
gradient and its determinant as well known in fluid-structure interaction.
For theoretical and numerical reasons, this functional 
needs to be regularized, including the control variable $q$, such that
\[
K(U,q) = k(U) + \frac{\alpha}{2}||q - q_0||,
\] 
where $\alpha$ is the Tikhonov parameter and $q_0$ some 
reference control.

The rest of the progam is similar to the previous optimization problems where
we formulate the state equation in a weak form $a(v,p)(\phi)$ such that the 
final problem reads
\[
K(U,q) \rightarrow 0 \quad \text{s.t.} \quad a(v,p)(\phi) = 0.
\]

>>>>

The target functional is considered as 
\[
k(U) = \int_{\hat\Gamma_O \cup \hat\Gamma_i} \hat n\cdot \hat J\hat\sigma(v,p)\hat
F^{-T} \cdot \hat d \, ds,
\]
where $\Gamma_O$ denotes the cylinder boundary and $\Gamma_i$ the 
interface between fluid and solid, and $\hat d$ is a vector in the
direction
of the mean flow. Moreover, $\hat J$ and $\hat F$ denote the deformation 
gradient and its determinant as well known in fluid-structure interaction.
For theoretical and numerical reasons, this functional 
needs to be regularized, including the control variable $q$, such that
\[
K(q,U) = k(U) + \frac{\alpha}{2}||q - q_0||,
\] 
where $\alpha$ is the Tikhonov parameter and $q_0$ some 
reference control.

The rest of the progam is similar to the previous optimization problems where
we formulate the state equation in a weak form $a(q,U)(\phi)$ such that the 
final problem reads
\[
K(q,U) \rightarrow \text{min} \quad \text{s.t.} \quad a(q,U)(\phi) = 0.
\]
